\documentclass{article}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{color}

\title{Educational Movie API User Manual}
\author{Development Team}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}
This document provides a user manual for the Educational Movie API. The API allows users to browse, search, and analyze educational and documentary movies.

\section{Base URL}
The API is hosted at: \texttt{http://localhost:8000}

\section{Endpoints}

\subsection{General}
\begin{itemize}
    \item \textbf{GET /}: Welcome message.
    \item \textbf{GET /docs}: Interactive API documentation (Swagger UI).
\end{itemize}

\subsection{Movies}
\begin{itemize}
    \item \textbf{GET /movies}: List movies with pagination.
    \begin{itemize}
        \item Parameters:
        \begin{itemize}
            \item \texttt{skip} (int, default=0): Number of records to skip.
            \item \texttt{limit} (int, default=10): Number of records to return.
        \end{itemize}
    \end{itemize}
    
    \item \textbf{GET /movies/\{movie\_id\}}: Get detailed information about a specific movie.
    \begin{itemize}
        \item Parameters:
        \begin{itemize}
            \item \texttt{movie\_id} (int): The ID of the movie.
        \end{itemize}
    \end{itemize}
\end{itemize}

\subsection{Search}
\begin{itemize}
    \item \textbf{GET /search}: Search movies by title.
    \begin{itemize}
        \item Parameters:
        \begin{itemize}
            \item \texttt{q} (str): Search query (min length 3).
        \end{itemize}
    \end{itemize}
\end{itemize}

\subsection{Analytics}
The following endpoints provide complex analytical insights:

\begin{itemize}
    \item \textbf{GET /analytics/popular-genres}: Top 5 most popular genres in documentaries.
    \item \textbf{GET /analytics/prolific-actors}: Actors who have appeared in multiple documentaries.
    \item \textbf{GET /analytics/avg-runtime-by-year}: Average runtime of documentaries by release year.
    \item \textbf{GET /analytics/flops}: Movies with high budget but low revenue.
    \item \textbf{GET /analytics/director-actors}: Directors who also acted in the same movie.
    \item \textbf{GET /analytics/top-production-countries}: Top production countries by number of movies.
    \item \textbf{GET /analytics/keyword-rich-movies}: Movies with the most keywords.
    \item \textbf{GET /analytics/history-war-movies}: Movies with more than 3 genres.
    \item \textbf{GET /analytics/best-year}: Year with the highest average vote (min 3 movies).
    \item \textbf{GET /analytics/multiskilled-crew}: Crew members who worked in more than one department.
\end{itemize}

\section{Error Handling}
The API returns standard HTTP status codes:
\begin{itemize}
    \item 200: Success
    \item 404: Not Found
    \item 422: Validation Error
    \item 500: Internal Server Error
\end{itemize}

\section{Poster Endpoint}

\subsection{Get Movie Poster}
\textbf{Endpoint:} \texttt{GET /movies/\{movie\_id\}/poster} \\
\textbf{Description:} Retrieves the poster image for a specific movie. \\
\textbf{Parameters:}
\begin{itemize}
    \item \texttt{movie\_id} (path): The ID of the movie.
\end{itemize}
\textbf{Response:} Returns the image file (JPEG) directly. Returns 404 if not found.

\end{document}

